---
title: "Preliminary Data Analysis"
author: "Sean Kent"
date: "10/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(odbc)
library(DBI)
library(tidyverse)
library(dbplyr)

```


```{r}
# odbc::odbcListDrivers()
# see https://db.rstudio.com/best-practices/drivers/ to install drivers

con <- dbConnect(odbc(), 
                 driver = "PostgreSQL Driver",
                 server = "database-2.clbsgd2qdkby.us-east-1.rds.amazonaws.com",
                 database = "postgres",
                 uid = "postgres",
                 pwd = askpass::askpass(),
                 port = 5432)

```

## Basic exploration of the sim_params table

```{r}
# odbc::dbExistsTable(con, "sim_params")
odbc::odbcListColumns(con, "sim_params")
```


```{r}
sim_params_db <- tbl(con, "sim_params")

colnames(sim_params_db)

sim_params_db %>% 
  distinct(contact_rates)

sim_params_db %>% 
  distinct(time_horizon)

sim_params_db %>% 
  distinct(group_index)

sim_params_db %>% 
  filter(sim_id == "eb7b24a6-8623-4fd1-af35-e94748ec65f8") %>% 
  distinct()

sim_params_db %>% 
  distinct(sim_id)

sim_params_db

```

- Not sure what this dataset is unique at.  The sim_id has about 160 rows for each, and there are 8 unique `contact_rates`, 8 unique `group_index`, which corresponds exactly with group_names. Actually, it appears that each sim_id corresponds only to 8 unique rows, so perhaps 160 corresponds to the 20 trajectories * 8 parameters info combos.  
- It seems like this is set up for potentially varying group contact rates parameters, but at the present moment there is only one set of contact rates used.  


## Basic exploration of the group_params table

```{r}
group_params_db <- tbl(con, "group_params")

colnames(group_params_db)

group_params_db %>% 
  filter(sim_id == "eb7b24a6-8623-4fd1-af35-e94748ec65f8") %>% 
  distinct()

group_params_db %>% 
  distinct(sim_id)


```

- Again here there appears to be some repeated rows going on.  Each sim_id only has 8 unique rows, but 160 rows total.  These 8 rows correspond to the parameters on the group (grad students, undergrad dorm, etc).  
- There are 31 distinct sim_ids, need to figure out which parameters are varied throughout. 

```{r}
# Which parameters are varied in the 31 different simulations?

all_params <- 
  group_params_db %>% 
  distinct() %>% 
  collect()

# Skim the dataset and filter for unique values

all_params_wide <-   
  all_params %>% 
  select(-scenario_name) %>% 
  pivot_wider(id_cols = sim_id,  
              names_from = group_number,
              values_from = c(everything(), -sim_id, -group_number)) %>% 
  mutate(across(everything(), ~ as.factor(.x)))

skim_df <- 
  all_params_wide %>% 
  skimr::skim() %>% 
  filter(factor.n_unique > 1)

skim_df
```

- Parameters varied:
  - initial_ID_prevalence
  - daily_outside_infection_p
  - test_protocol_QFNR
  
It seems like the parameters are varied for all groups 0-7.  


```{r}
all_params_wide %>% 
  select(skim_df$skim_variable) 

all_params_wide %>% 
  select(skim_df$skim_variable) %>% 
  select(starts_with("initial_ID_prevalence")) %>% 
  distinct()


all_params_wide %>% 
  select(skim_df$skim_variable, -sim_id) %>% 
  distinct()

all_params_wide %>% 
  select(skim_df$skim_variable, -sim_id) %>% 
  arrange_all()
```

<!-- More detail on how the parameters are varied: -->

<!-- - For `initial_ID_prevalence`, there are 11 unique combinations -->
<!--   - Group 0 (UGD): there are 4 unique values: 0.00294, 0.00090, 0.00274, 0.00027. -->
<!--     - The most common value is 0.00294 -->
<!--   - Group 1 (UGOC): there are 4 unique values: 0.00090, 0.00973, 0.00274, 0.00027. -->
<!--     - The most common value is 0.00973, the other values happen once -->
<!--   - Group 2 (GSR): there are 2 unique values: 0.03297, 0.00027, 0.00090, 0.00027. -->
<!--     - The most common value is 0.03297, the other value happens once -->
<!--   - Group 3 (GSO): there are 2 unique values: 0.03297, 0.00027 -->
<!--     - The most common value is 0.03297, the other value happens once -->
<!-- - For `daily_outside_infection_p`, there are 7 unique combinations -->
<!--   - For groups 0, 1, 2, there are 3 unique values: 1.2e-5, 1.5e-4, 3.0e-4 -->
<!--     - The most common value is 1.2e-5. -->
<!--     - The other values happen once in each combination, and there is one setting where all are set to 1.2e-5 -->
<!-- - For `test_protocol_QFNR`, there are 4 unique combinations -->
<!--   - For group 0, 1, 2, there are 2 unique values: 0.1, 0.3 -->
<!--   - The common value is 0.1 -->
<!--   - Values are changed to 0.3 for one group in each setting.   -->

<!-- Ignoring sim_id, it seems like there are actually only 20 unique parameter combinations.  There is a group of 12 sim_ids that only represent 1 combination of the parameter settings, and they are the most common.   -->


## Basic exploration of the results table

```{r}
results_db <- tbl(con, "results")

colnames(results_db)

results_db %>% 
  filter(sim_id == "eb7b24a6-8623-4fd1-af35-e94748ec65f8",
         replicate_id == "53d853b7-a01e-491c-82c3-2afaf1e7192f",
         group_number == 0,
         t == 112) 

results_db %>% 
  distinct(replicate_id) 

results_db %>% 
  distinct(sim_id)

n_sim <- results_db %>% distinct(sim_id) %>% collect() %>% nrow()
n_groups <- results_db %>% distinct(group_number) %>% collect() %>% nrow()


results_db %>% 
  select(sim_id, group_number, replicate_id, t)
# assume that replicate_ids are incorrect, and 

# results_db %>% 
#   mutate(replicate_id = paste0(replicate_id, "-", ) %>% 
#   show_query()

```

- There are exactly 31 replicate ids, and it seems like there is one for each sim_id.  What is the difference between the two?  
- Consequently, there is not a unique id for each trajectory of the simulation (that I can see), how to group on this to calculate peak and time to peak??
- Seems like there are 20 trajectories for each of the sim_id, replicate_id combinations.  

TODO: wait for Steve to respond about the replicate grouping variable before proceeding further. 

