---
title: "Initial Simulation Summary"
author: "Sean Kent"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    cache = FALSE,
    warning = FALSE,
    message = FALSE,
    fig.align = "center"
)

library(odbc)
library(DBI)
library(here)
library(tidyverse)
library(dbplyr)
library(knitr)
library(kableExtra)
library(ggbeeswarm)

# Tables
kable_standard <- function(...) {
    kable(booktabs = TRUE, linesep = "", ...) %>% 
        kable_styling(full_width = FALSE)
}

options(knitr.kable.NA = '')

```


```{r}
# odbc::odbcListDrivers()
# see https://db.rstudio.com/best-practices/drivers/ to install drivers

db <- config::get("dbtest")

con <- dbConnect(RPostgres::Postgres(),
                 dbname = db$dbname,
                 host = db$host,
                 port = db$port,
                 user = db$user,
                 password = db$password)

```


## Parameters that were varied

```{r}
sim_params_db <- tbl(con, "sim_params")
n_sim <- sim_params_db %>% distinct(sim_id) %>% collect() %>% nrow()

# n_trajectories <- sim_params_db %>% distinct(ntrajectories) %>% collect() %>% unique()

sim_params_db %>% 
  distinct(sim_id, ntrajectories) %>% 
  count(ntrajectories) %>% 
  arrange(ntrajectories) %>% 
  kable_standard(caption = "Summary of number of trajectories by simulation id")


# sim_params_db %>% 
#   distinct(sim_id, ntrajectories)

```

Overall, there were `r n_sim` distinct simulation settings.  The number of trajectories for each setting is given above.  

```{r}
sim_params_db <- tbl(con, "sim_params")
group_names <- sim_params_db %>% 
  # filter(ntrajectories == 2) %>% 
  # filter(ntrajectories %in% c(1, 3, 20)) %>% 
  distinct(group_index, group_names) %>% 
  collect() %>% 
  mutate(group_index = as.character(group_index))

```


```{r}

group_params_db <- tbl(con, "group_params")

all_params <-
  group_params_db %>%
  distinct() %>%
  collect()

# Skim the dataset and filter for unique values

all_params_wide <-
  all_params %>%
  select(-`_scenario_name`) %>%
  pivot_wider(id_cols = sim_id,
              names_from = group_number,
              values_from = c(everything(), -sim_id, -group_number)) %>%
  mutate(across(everything(), ~ as.factor(.x)))

# write_csv(all_params_wide2, here("data/2020-10-19_all-params-wide.csv"))
# all_params_wide <- read_csv(here("data/2020-10-19_all-params-wide.csv")) %>% 
#   mutate(across(where(is.double), as.factor))


skim_df <- 
  all_params_wide %>% 
  skimr::skim() %>% 
  filter(factor.n_unique > 1)

# skim_df

all_params_wide %>% 
  select(sim_id, skim_df$skim_variable) %>% 
  pivot_longer(cols = -sim_id) %>% 
  group_by(name) %>% 
  summarize(value = unique(value)) %>% 
  pivot_wider() %>% 
  pivot_longer(cols = everything(), 
               names_to = c("variable", "Group"),
               names_pattern = "(.*)_([:digit:])") %>% 
  pivot_wider(names_from = variable,
              values_from = value) %>% 
  mutate(across(.cols = -Group, .fns = ~map(.x, ~scales::number(as.numeric(as.character(sort(.x))))))) %>% 
  left_join(group_names, by = c("Group" = "group_index")) %>% 
  select(Group, group_names, everything()) %>% 
  # mutate_all(as.character) %>% 
  kable_standard() %>% 
  add_header_above(c(" " = 2, "Varied Parameters" = 3))



```




## Key metrics

The metrics evaluated here are 

- **peak** - what is the highest number reached over the time span
- **time to peak** - at what time does the peak happen
- **cumulative numbers** - what is the total number over the trajectory

Note: I'm not 100% sure how to get cumulative numbers for the quarantine population, since people are counted in quarantine over multiple time periods.  


## Results - Peak isolation capacity


```{r}

file_name <- here("data/2020-10-27_summary-of-results_quarantine.csv")

if (file.exists(file_name)) {
  df <- read_csv(file_name)
} else {
  # Query the database to pull the new results
  results_db <- tbl(con, "results")
  # colnames(results_db)
  
  # create a table that averages over the sim_id and group 
  dbGetQuery(con,
             '
           CREATE TEMP TABLE results_averaged AS
           SELECT "sim_id", "replicate_id", "t", "group_number", AVG("QS")  + AVG("QI") AS "Q"
           FROM "results"
           GROUP BY "sim_id", "replicate_id", "t", "group_number"
           ')           
  
  # now calculate peak and time to peak 
  df <- 
    dbGetQuery(con, '
           SELECT a.*
           FROM results_averaged a
           INNER JOIN
             (SELECT "sim_id", "group_number", MAX("Q") AS "peak"
             FROM results_averaged 
             GROUP BY "sim_id", "group_number") b
           ON a.sim_id = b.sim_id 
           AND a.group_number = b.group_number 
           AND a."Q" = b."peak" ')
  
  df <- 
    df %>% 
    group_by(sim_id, group_number) %>% 
    filter(t == min(t)) %>% 
    ungroup()
  
  dbGetQuery(con, "DROP TABLE IF EXISTS results_averaged")
  
  pop_sizes <- all_params %>% distinct(group_number, population_size)
  
  df <- 
    df %>% 
    left_join(pop_sizes, by = "group_number") %>% 
    mutate(Q_frac = Q / population_size)
  
  write_csv(df, file_name)
}

```



```{r}
df2 <- 
  df %>% 
  left_join(all_params_wide %>% 
              select(sim_id, skim_df$skim_variable),
            by = "sim_id") %>% 
  left_join(group_names %>% mutate(group_index = as.integer(group_index)),
            by = c("group_number" = "group_index"))

df2 <- df2 %>% 
  mutate(across(c("t", "group_number"), as.double))

# colnames(df2)
# dim(df2)
```

### Overview and Context 

```{r}
df2 %>% 
  mutate(group = paste0(group_number, ": ", group_names)) %>%
  ggplot(aes(t, Q)) +
  geom_quasirandom(aes(color = as.factor(group)), alpha = 0.5) +
  scale_color_viridis_d(name = "Group", option = "B", begin = 0.2, end = 0.8) +
  labs(x = "Time of Peak Quarantine", y = "Quarantine Size at Peak",
       title = "Summary of Peak vs Time of Peak in all simulations")

```

<!-- Overall, there's more variation in the time of peak than the peak.  In fact, there's very little variation in the peak among all of the simulation settings.   -->


```{r}
df2 %>% 
  mutate(group = paste0(group_number, ": ", group_names)) %>% 
  ggplot(aes(t, Q_frac)) +
  # ggplot(aes(t, Q)) +
  geom_quasirandom(aes(color = as.factor(group))) +
  # facet_wrap(~ as.factor(group), scales = "free_y") +
  facet_wrap(~ as.factor(group)) +
  scale_color_viridis_d(option = "B", begin = 0.2, end = 0.8) +
  labs(x = "Time of Peak Quarantine", y = "Fraction of Population in Quarantine at Peak ",
       title = "Time of Peak vs Fraction in Quarantine at Peak in All Simulations",
       subtitle = "Split by Groups") +
  theme(legend.position = "none")

  
```

<!-- Looking deeper at the fraction of population in quarantine, we can see that Grads/Undergrads have higher fractions in quarantine, but there still isn't much variation.  Changing the time to peak seems only to delay the inevitable in this model.  There are a few simulations of note in the fac/staff groups and Madison community where the time of peak is significantly delayed.  Look deeper into this -->



```{r}
plot_fun <- function(data, y, fill, y_lab = NULL) {
  data %>% 
    # mutate(group = paste0(group_number, ": ", group_names)) %>% 
    ggplot(aes_(~as.factor(group_number), as.name(y), fill = as.name(fill))) +
    # geom_violin(draw_quantiles = seq(0, 1, by = 0.25), scale = "width", color = "grey50") +
    geom_quasirandom(aes_(color = as.name(fill)), dodge.width = 0.5) +
    stat_summary(aes_(color = as.name(fill)), geom = "point", shape = 3) +
    geom_hline(yintercept = 0) +
    
    scale_fill_viridis_d(option = "magma", end = 0.8, begin = 0.2, aesthetics = c("color", "fill")) +
    theme_minimal() +
    theme(legend.position = "bottom") +
    labs(x = "Group",
         y = y_lab,
         title = fill) 

}

vars_to_plot <- setdiff(skim_df$skim_variable, "sim_id")
```


### Fraction in Quarantine at Peak

Look across changes to a single parameter 


```{r}
plots <- map(vars_to_plot, ~plot_fun(df2, y = "Q_frac", fill = .x,
                                     y_lab = "Fraction of Population in Quarantine at Peak") +
               scale_y_continuous(labels = scales::percent))

walk(plots, print)


```

### Time of peak quarantine capacity 

Look across changes to a single parameter 

```{r}
plots <- map(vars_to_plot, ~plot_fun(df2, y = "t", fill = .x,
                                     y_lab = "Time of Peak") )

walk(plots, print)

```





```{r, eval = FALSE}
## Check what constitutes the entire population
results_db %>% 
  mutate(total_pop = S + QS + QI + R + 
           E_0 + E_1 + E_2 + E_3 + E_4 + E_5 + E_6 + 
           pre_ID_0 + pre_ID_1 + pre_ID_2 + pre_ID_3 + 
           ID_0 + ID_1 + ID_2 + ID_3 + ID_4 + ID_5 + ID_6 + ID_7 + 
           SyID_mild_0 + SyID_mild_1 + SyID_mild_2 + SyID_mild_3 + SyID_mild_4 + SyID_mild_5 + SyID_mild_6 + SyID_mild_7 + SyID_mild_8 + SyID_mild_9 + SyID_mild_10 + SyID_mild_11 + SyID_mild_12 + SyID_mild_13 + SyID_mild_14 + SyID_mild_15 + SyID_mild_16 + SyID_mild_17 + SyID_mild_18 + SyID_mild_19 + 
           SyID_severe_0 + SyID_severe_1 + SyID_severe_2 + SyID_severe_3 + SyID_severe_4 + SyID_severe_5 + SyID_severe_6 + SyID_severe_7 + SyID_severe_8 + SyID_severe_9 + SyID_severe_10 + SyID_severe_11 + SyID_severe_12 + SyID_severe_13 + SyID_severe_14 + SyID_severe_15 + SyID_severe_16 + SyID_severe_17 + SyID_severe_18 + SyID_severe_19) %>% 
  select(group_number, t, total_pop, everything()) 

# total with covid is everything except S, QS, and R 
# can pull cumulative numbers for the cumulative thing 


```

***


## Results - Peak of population with COVID


```{r}

file_name <- here("data/2020-10-27_summary-of-results_covid.csv")

if (file.exists(file_name)) {
  df <- read_csv(file_name)
} else {
  # Query the database to pull the new results
  results_db <- tbl(con, "results")
  # colnames(results_db)
  
  # create a table that averages over the sim_id and group 
  dbGetQuery(con,
             '
           CREATE TEMP TABLE results_averaged AS
           SELECT "sim_id", "replicate_id", "t", "group_number", 
           "cumulative_mild" + "cumulative_severe" + "cumulative_outside_infections" AS "cumulative_covid_pop", 
           "QI" + "E_0" + "E_1" + "E_2" + "E_3" + "E_4" + "E_5" + "E_6" + "pre_ID_0" + "pre_ID_1" + "pre_ID_2" + "pre_ID_3" + "ID_0" + "ID_1" + "ID_2" + "ID_3" + "ID_4" + "ID_5" + "ID_6" + "ID_7" + "SyID_mild_0" + "SyID_mild_1" + "SyID_mild_2" + "SyID_mild_3" + "SyID_mild_4" + "SyID_mild_5" + "SyID_mild_6" + "SyID_mild_7" + "SyID_mild_8" + "SyID_mild_9" + "SyID_mild_10" + "SyID_mild_11" + "SyID_mild_12" + "SyID_mild_13" + "SyID_mild_14" + "SyID_mild_15" + "SyID_mild_16" + "SyID_mild_17" + "SyID_mild_18" + "SyID_mild_19" + "SyID_severe_0" + "SyID_severe_1" + "SyID_severe_2" + "SyID_severe_3" + "SyID_severe_4" + "SyID_severe_5" + "SyID_severe_6" + "SyID_severe_7" + "SyID_severe_8" + "SyID_severe_9" + "SyID_severe_10" + "SyID_severe_11" + "SyID_severe_12" + "SyID_severe_13" + "SyID_severe_14" + "SyID_severe_15" + "SyID_severe_16" + "SyID_severe_17" + "SyID_severe_18" + "SyID_severe_19" AS "covid_pop"
           FROM "results"
           ')           
  
  # now calculate peak and time to peak 
  df <- 
    dbGetQuery(con, '
           SELECT a.*
           FROM results_averaged a
           INNER JOIN
             (SELECT "sim_id", "group_number", MAX("covid_pop") AS "peak"
             FROM results_averaged 
             GROUP BY "sim_id", "group_number") b
           ON a.sim_id = b.sim_id 
           AND a.group_number = b.group_number 
           AND a."covid_pop" = b."peak" ')
  
  df <- 
    df %>% 
    group_by(sim_id, group_number) %>% 
    filter(t == min(t)) %>% 
    ungroup()
  
  dbGetQuery(con, "DROP TABLE IF EXISTS results_averaged")
  
  pop_sizes <- all_params %>% distinct(group_number, population_size)
  
  df <- 
    df %>% 
    left_join(pop_sizes, by = "group_number") %>% 
    mutate(covid_frac = covid_pop / population_size,
           cumulative_covid_frac = cumulative_covid_pop / population_size)
  
  write_csv(df, file_name)
}

```



```{r}
df2 <- 
  df %>% 
  left_join(all_params_wide %>% 
              select(sim_id, skim_df$skim_variable),
            by = "sim_id") %>% 
  left_join(group_names %>% mutate(group_index = as.integer(group_index)),
            by = c("group_number" = "group_index"))

df2 <- df2 %>% 
  mutate(across(c("t", "group_number"), as.double))

# colnames(df2)
# dim(df2)
```


### Overview and Context 

```{r}
df2 %>% 
  mutate(group = paste0(group_number, ": ", group_names)) %>%
  ggplot(aes(t, covid_pop)) +
  geom_quasirandom(aes(color = as.factor(group)), alpha = 0.5) +
  scale_color_viridis_d(name = "Group", option = "B", begin = 0.2, end = 0.8) +
  labs(x = "Time of Peak COVID", y = "Covid Prevalence at Peak",
       title = "Summary of Peak vs Time of Peak in all simulations")

```

<!-- Overall, there's more variation in the time of peak than the peak.  In fact, there's very little variation in the peak among all of the simulation settings.   -->


```{r}
df2 %>% 
  mutate(group = paste0(group_number, ": ", group_names)) %>% 
  ggplot(aes(t, covid_frac)) +
  # ggplot(aes(t, Q)) +
  geom_quasirandom(aes(color = as.factor(group))) +
  # facet_wrap(~ as.factor(group), scales = "free_y") +
  facet_wrap(~ as.factor(group)) +
  scale_color_viridis_d(option = "B", begin = 0.2, end = 0.8) +
  labs(x = "Time of Peak COVID cases", y = "Fraction of Population w/ COVID at Peak ",
       title = "Time of Peak vs Fraction w/ COVID at Peak in All Simulations",
       subtitle = "Split by Groups") +
  theme(legend.position = "none")

  
```



### Percentage with COVID at Peak

Look across changes to a single parameter 


```{r}
plots <- map(vars_to_plot, ~plot_fun(df2, y = "covid_frac", fill = .x,
                                     y_lab = "Percentage with COVID at Peak") +
               scale_y_continuous(labels = scales::percent))

walk(plots, print)


```

### Time of peak covid 

Look across changes to a single parameter 


```{r}
plots <- map(vars_to_plot, ~plot_fun(df2, y = "t", fill = .x,
                                     y_lab = "Time of Peak COVID prevalence")) 

walk(plots, print)


```

### Cumulative Percentage with COVID at end

Look across changes to a single parameter 


```{r}
plots <- map(vars_to_plot, ~plot_fun(df2, y = "cumulative_covid_frac", fill = .x,
                                     y_lab = "Cumulative Percentage with COVID at end") +
               scale_y_continuous(labels = scales::percent))

walk(plots, print)


```





